Continuous voting by approval and participation

### 2015-04-24 ApresentacoesArtigos/collectiveRanking/paper.tex
abstract enhancement

\begin{abstract}
In finding the adequate way to prioritize proposals, the Brazilian participation community agreed about two indexes of approval and of participation.
Both practice and literature is constantly handled by the experts involved, and the formalization of such model and metrics seems novel.
Also, the relevance of this report is strengthened by the nearby use of these indexes by the Brazilian General Secretariat of the Republic to raise and prioritize proposals about public health care in open processes.
\end{abstract}

>>>>

\begin{abstract}
In finding the adequate way to prioritize proposals, the Brazilian participation community agreed about the measurement of two indexes, one of approval and one of participation.
Both practice and literature is constantly handled by the experts involved, and the formalization of such model and metrics seems novel.
Also, the relevance of this report is strengthened by the nearby use of these indexes by the Brazilian General Secretariat of the Republic to raise and prioritize proposals about public health care in open processes.
\end{abstract}
